Output Summary

### 2023-05-11 03-post-process/output-plots-children/10-rho-params.Rmd
Remove time-varying prespawn mort from all output plots

# assign names to the different rho parameters
rho_labels = c(
  "rho_Lphi_E_Pb" = "Egg-to-Parr Survival",
  "rho_Lphi_O0_O1" = "Yr1 Ocean Survival",
  "rho_Lpsi_O1" = "Pr(Mature Age-3)",
  "rho_Lpsi_O2" = "Pr(Mature Age-4)",
  "rho_lDelta_L_Pb_Mb" = "'Growth' Factor",
  "rho_Lphi_Mb_Ma" = "Trib. to LGR Survival",
  "rho_lL_Pb" = "Mean Parr Length",
  "rho_Lphi_Pa_Mb" = "Overwinter Survival",
  "rho_Lphi_Sb_Sa" = "Pre-spawn Survival",
  "rho_Lphi_Rb_Ra" = "BON -> LGR Survival",
  "rho_Lpi" = "Pr(Fall Migrant)",
  "rho_Lphi_Ma_O0" = "LGR -> Ocean Survival"
)
```

@@

### Pre-Spawn Survival

```{r rho_Lphi_Sb_Sa-plot, fig.height = rho_mat_fig_h, fig.width = rho_mat_fig_w}
rho_mat_plots("rho_Lphi_Sb_Sa[")
```

>>>>

# assign names to the different rho parameters
rho_labels = c(
  "rho_Lphi_E_Pb" = "Egg-to-Parr Survival",
  "rho_Lphi_O0_O1" = "Yr1 Ocean Survival",
  "rho_Lpsi_O1" = "Pr(Mature Age-3)",
  "rho_Lpsi_O2" = "Pr(Mature Age-4)",
  "rho_lDelta_L_Pb_Mb" = "'Growth' Factor",
  "rho_Lphi_Mb_Ma" = "Trib. to LGR Survival",
  "rho_lL_Pb" = "Mean Parr Length",
  "rho_Lphi_Pa_Mb" = "Overwinter Survival",
  "rho_Lphi_Rb_Ra" = "BON -> LGR Survival",
  "rho_Lpi" = "Pr(Fall Migrant)",
  "rho_Lphi_Ma_O0" = "LGR -> Ocean Survival"
)
```

@@

### 2023-05-11 03-post-process/output-plots-children/12-param-summaries.Rmd
Remove time-varying prespawn mort from all output plots

```{r prespawn-surv-bxp, fig.width = p3_width, fig.height = p3_height}
mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
my_boxplot("mu_phi_Sb_Sa", "Average Survival", ylim = ylim_01)
my_boxplot("sig_Lphi_Sb_Sa[", "Process SD", ylim = c(0,2))
my_boxplot(paste0("rho_Lphi_Sb_Sa", vcov_inds), "Correlation", ylim = c(-1,1), ticklab = vcov_labels); ref_line(h = 0)
```

>>>>

```{r prespawn-surv-bxp, fig.width = p4_width, fig.height = p4_height, out.width = "50%"}
mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
my_boxplot("mu_phi_Sb_Sa", "Average Survival", ylim = ylim_01)
```
